An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-15 paper/paper.tex
Paper: Start of proofreading

In the client-server model, servers are expected to always be available and accessible. Peer to peer networks do not have this luxury. Instead, they experience the constant fluctuation of peers joining and leaving the network. This is called \textit{churn} \cite{StorageSearchP2PNetworks}. Churn in P2P networks complicates the communication between peers because the sought peer may be offline. This is especially a problem in P2P backup systems, for example, when trying to recover data from a peer who is not online. The strategies for dealing with churn, and many other P2P-specific complications, heavily depend on the type of overlay network a P2P application uses. We discuss churn in more detail in section \ref{sec:churn}.

@@

An overlay network is a network built on top of another network. That is, an overlay network consists of nodes with neighbors who are not physically connected, but instead use the underlying network to establish a virtual connection. They need not be constrained by the limitations of the physical world. Consider a trivial example where there are three computers connected to the Internet, but located in different parts of the world. These three computers could form an overlay network by agreeing to be virtual neighbors to each other. If their overlay network was used in a P2P application, then, when connecting to each other, they will use the underlying network, the Internet, to actually send messages. The P2P application does not need to know about the underlying network that is used to route messages, it only needs to know that there is an overlay network that defines the direct connections between peers.

Peer to peer applications use overlay networks as their foundation.\footnote{Overlay networks are used for many purposes, not just P2P applications. Note, however, in discussing overlay networks, we will still refer to their participants as \textit{peers}.}  The P2P overlay network provides peers the ability to join and leave the network and find other peers with whom to communicate.

@@

To join a structured overlay network, a peer must know at least one other peer already in the network. This peer is often called the \textit{bootstrap peer}. The joining peer will contact the bootstrap peer to find its proper place in the topology. We come back to this in more detail in the explanation of how to find other peers, below.

>>>>

In the client-server model, servers are expected to always be available and accessible. Peer to peer networks do not have this luxury. Instead, they experience the constant fluctuation of peers joining and leaving the network. This is called \textit{churn} \cite{StorageSearchP2PNetworks}. Churn in P2P networks complicates the communication between peers because the sought peer may be offline. This is especially a problem in P2P backup systems; for example, a peer might try to recover data from another peer who is not online. The strategies for dealing with churn, and many other P2P-specific complications, heavily depend on the type of overlay network a P2P application uses. We discuss churn in more detail in section \ref{sec:churn}.

@@

An overlay network is any network built on top of another network. That is, an overlay network consists of nodes with neighbors who are not physically connected, but instead use the underlying network to establish a virtual connection. They need not be constrained by the limitations of the physical world. Consider a trivial example where there are three computers connected to the Internet, but located in different parts of the world. These three computers could form an overlay network by agreeing to be virtual neighbors to each other. If their overlay network was used in a P2P application, then, when connecting to each other, they will use the underlying network, the Internet, to actually send messages. The P2P application does not need to know about the underlying network that is used to route messages; it only needs to know that there is an overlay network that defines the direct connections between peers.

Peer to peer applications use overlay networks as their foundation.\footnote{Overlay networks are used for many purposes, not just P2P applications. Note, however, in discussing overlay networks, we will still refer to their participants as \textit{peers}.}  The P2P overlay network provides structure for the application that uses it, allowing peers to find each other.

@@

To join a structured overlay network, a peer must know at least one other peer already in the network. This peer is often called the \textit{bootstrap peer}. The joining peer will contact the bootstrap peer to find its proper place in the topology. We come back to this below in more detail in our explanation of how to find other peers.
